Online Multiclass Linear Classification with Bandit Feedback

### 2018-11-26 arxiv-version/main.tex
State the polynomial approximation theorem

% Math symbols and commands
\newcommand{\R}{\mathbb{R}}  % set of real numbers
\newcommand{\indicator}[1]{\mathbf{1}\left[#1 \right]} % indicator
\newcommand{\ip}[2]{\left\langle #1, #2 \right\rangle} % inner product
\newcommand{\norm}[1]{\left\| #1 \right\|}  % norm of a vector or a matrix
\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\Exp}{\mathbf{E}}  % expected value

@@

We construct several different mappings $\phi$. The parameters $R'$ and
$\gamma'$ for the different mappings are essentially the same. However, one
mapping has the advantage of having a kernel $k(x,x')$ that is faster to
evaluate. Another mapping has the advantage that one does \emph{not} need to
know the initial margin $\gamma$. In other words, the same mapping works for all
possible values of $\gamma > 0$. The idea behind all the mappings is that
polynomials are universal function approximators, which is a well known fact
expressed by the classical Stone-Weierstrass theorem~\citep[page 159]{Rudin-1976}.

>>>>

% Math symbols and commands
\newcommand{\R}{\mathbb{R}}  % set of real numbers
\newcommand{\indicator}[1]{\mathbf{1}\left[#1 \right]} % indicator
\newcommand{\ip}[2]{\left\langle #1, #2 \right\rangle} % inner product
\newcommand{\norm}[1]{\left\| #1 \right\|}  % norm of a vector or a matrix
%\DeclareMathOperator*{\deg}{deg}
\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\Exp}{\mathbf{E}}  % expected value

@@

We construct several different mappings $\phi$. The parameters $R'$ and
$\gamma'$ for the different mappings are not the same, but the ratios
$R'/\gamma'$ are qualitively the same. However, one mapping has the advantage of
having a kernel $k(x,x')$ that is faster to evaluate. Another mapping has the
advantage that one does \emph{not} need to know the initial margin $\gamma$. In
other words, the same mapping works for all possible values of $\gamma > 0$.

The idea behind all the mappings is that, on a compact set, multivariate
polynomials uniformly approximate any continuous function. This is result is a
special case of the well known Stone-Weierstrass theorem~\citep[Section
10.10]{Davidson-Donsig-2010}. In our case, we use a multivariate polynomial to
approximate the indicator function corresponding to the intersection of $K-1$
halfspaces. This polynomial separates examples in one class from examples in the
other classes. To be able to quantify $\gamma'$ and $R'$ as well as time
complexity of evaluating $k(x,x')$ we need to quantify certain parameters
of the approximating polynomial (degree, norm, range of values).
The parameters are quantified in \autoref{theorem:polynomial-approximation}
stated below.

Before we state the theorem, recall that a polynomial of $d$ variables is a
function $p:\R^d \to \R$ of the form
$$
p(x) = p(x_1, x_2, \dots, x_d) = \sum_{i_1, i_2, \dots, i_d} c_{i_1, i_2, \dots, i_d} x_1^{i_1} x_2^{i_2} \dots x_d^{i_d}
$$
where the sum ranges over a finite set of tuples $(i_1, i_2, \dots, i_d)$ of
non-negative integers and $c_{i_1, i_2, \dots, i_d}$ is a real coefficient. The
\emph{degree} of a polynomial $p$, denoted by $\deg(p)$, is the largest value of
$i_1 + i_2 + \dots + i_d$ for which the coefficient is non-zero. The \emph{norm
of a polynomial} $p$ is defined as
$$
\norm{p} = \sqrt{\sum_{i_1, i_2, \dots, i_d} \left(c_{i_1, i_2, \dots, i_d} \right)^2 } \; .
$$

\begin{theorem}
\label{theorem:polynomial-approximation}
Let $w_1, w_2, \dots, w_K \in \R^d$ be such that $\sum_{i=1}^K \norm{w_1}^2 \le 1$.
Let $\gamma > 0$. There exists a polynomial $p:\R^d \to \R$ such that
\begin{itemize}
\item $p(x) \ge 1$ for all $x \in \bigcap_{i=2}^K \{ x \in \R^d ~:~ \ip{w_1}{x} \ge \ip{w_i}{x} + \gamma \}$
\item $p(x) \le -1$ for all $x \in \bigcup_{i=2}^K \{ x \in \R^d ~:~ \ip{w_1}{x} \le \ip{w_i}{x} - \gamma \}$
\item $\deg(p) \le ???$
\item $\norm{p} \le ???$
\item $|p(x)| \le ???$ for all $x \in \R^d$ such that $\norm{x} \le 1$
\end{itemize}
\end{theorem}
